### 2020-07-21 article.tex
Proper reference

\section{Introduction}
Computational science and engineering today enjoys unprecedented opportunities to transform
the way society solves many of its most urgent technological problems through predictive simulations.
At the heart of simulations are robust and scalable solution algorithms, and the efficient
production of applications requires a rich ecosystem of state-of-the-art
reusable libraries from which domain
specialists can benefit \cite{Bartlett:2017:XFT}. In this paper, we focus on the interoperability of two such
libraries.

On the one hand, PETSc \cite{balay1997cient}, the
Portable and Extensible Toolkit for Scientific computation, is a
well-established, actively developed software from the community. It may be used to efficiently
discretize partial differential equations and solve algebraic linear or
nonlinear systems of time-dependent equations. Among its strengths, it offers many
advanced features regarding preconditioning and tailored matrix formats, and it can
interact with third-party libraries, such as
\emph{hypre}~\cite{falgout2002hypre} for linear solvers, TetGen~\cite{si2013tet}
for mesh generation, p4est~\cite{BursteddeWilcoxGhattas11} for adaptive mesh
refinement, to cite a few. The extensibility and robustness of the framework
convinced computational scientists to use PETSc as one of the discretization and/or algebraic backend in
many different higher-level projects, see \url{https://www.mcs.anl.gov/petsc} for a comprehensive list.

@@

\bibitem{balay1997cient}
{\sc S.~Balay, W.~D. Gropp, L.~Curfman~McInnes, and B.~F. Smith}, {\em
  Efficient management of parallelism in object-oriented numerical software
  libraries}, Modern Software Tools in Scientific Computing,  (1997),
  pp.~163--202.

@@

\bibitem{cusparse-web-page}
{\sc NVIDIA}, {\em {cuSPARSE} web page}.
\newblock \url{https://docs.nvidia.com/cuda/cusparse/}, 2020.

@@

\bibitem{saad2003iterative}
{\sc Y.~Saad}, {\em {Iterative Methods for Sparse Linear Systems, Second
  Edition}}, SIAM, 2003.

>>>>

\section{Introduction}
Computational science and engineering today enjoys unprecedented opportunities to transform
the way society solves many of its most urgent technological problems through predictive simulations.
At the heart of simulations are robust and scalable solution algorithms, and the efficient
production of applications requires a rich ecosystem of state-of-the-art
reusable libraries from which domain
specialists can benefit~\cite{Bartlett:2017:XFT}. In this paper, we focus on the interoperability of two such
libraries.

On the one hand, PETSc~\cite{petsc-web-page,petsc-user-ref}, the
Portable and Extensible Toolkit for Scientific computation, is a
well-established, actively developed software from the community. It may be used to efficiently
discretize partial differential equations and solve algebraic linear or
nonlinear systems of time-dependent equations. Among its strengths, it offers many
advanced features regarding preconditioning and tailored matrix formats, and it can
interact with third-party libraries, such as
\emph{hypre}~\cite{falgout2002hypre} for linear solvers, TetGen~\cite{si2013tet}
for mesh generation, p4est~\cite{BursteddeWilcoxGhattas11} for adaptive mesh
refinement, to cite a few. The extensibility and robustness of the framework
convinced computational scientists to use PETSc as one of the discretization and/or algebraic backend in
many different higher-level projects, see \url{https://www.mcs.anl.gov/petsc} for a comprehensive list.

@@

\bibitem{petsc-user-ref}
{\sc S.~Balay, S.~Abhyankar, M.~F. Adams, J.~Brown, P.~Brune, K.~Buschelman,
  L.~Dalcin, A.~Dener, V.~Eijkhout, W.~D. Gropp, D.~Karpeyev, D.~Kaushik, M.~G.
  Knepley, D.~A. May, L.~C. McInnes, R.~T. Mills, T.~Munson, K.~Rupp, P.~Sanan,
  B.~F. Smith, S.~Zampini, H.~Zhang, and H.~Zhang}, {\em {PETS}c users manual},
  Tech. Report ANL-95/11 - Revision 3.13, Argonne National Laboratory, 2020.

\bibitem{petsc-web-page}
{\sc S.~Balay, S.~Abhyankar, M.~F. Adams, J.~Brown, P.~Brune, K.~Buschelman,
  L.~Dalcin, A.~Dener, V.~Eijkhout, W.~D. Gropp, D.~Karpeyev, D.~Kaushik, M.~G.
  Knepley, D.~A. May, L.~C. McInnes, R.~T. Mills, T.~Munson, K.~Rupp, P.~Sanan,
  B.~F. Smith, S.~Zampini, H.~Zhang, and H.~Zhang}, {\em {PETS}c web page},
  2020, \url{http://www.mcs.anl.gov/petsc}.

@@

\bibitem{cusparse-web-page}
{\sc NVIDIA}, {\em {cuSPARSE} web page}.
\newblock \url{https://docs.nvidia.com/cuda/cusparse}, 2020.

@@

\bibitem{saad2003iterative}
{\sc Y.~Saad}, {\em {Iterative Methods for Sparse Linear Systems}}, SIAM,
  second~ed., 2003.
